---
title: "Introduction to tiDML"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to tiDML}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r knit-options, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# First pass with tiDML

In the simplest case, you can use the package under complete default settings. Pick a model, specify data, outcome variable, treatment variable, and covariates, and hit go. Currently, the default models available are:
+ `dml_rf()` for random forest, and
+ `dml_nnet()` for a neural network.

Here I print the average treatment effect (ATE) of `am` on `mpg` in the `mtcars` dataset, controlling for all other variables as covariates. We use random forests (`rf`) for both nuisance models.

```{r simple}
library(tiDML)

fit_rf <- dml_rf(
  data = df,
  y = "price",
  d = "D",
  x = c("carat", "depth", "table", "x", "y", "z"),
)
print(random_forest_fitted)

```
The string `rf` is a shortcut for using the `ranger` package to fit random forest models. Other options include `lasso`, `ridge`, `enet`, `xgboost`, and `nnet`. See ' for LINK to MAN for the enging/model types available as default.

Printing out the recipe steps of the DML estimate shows the preprocessing steps that were automatically applied to the data before fitting the nuisance models. In this case, 
+ zero variance filtering,
+ Median imputation for missing values,
+ Dummy encoding for categorical variables, and
+ Centering and scaling of numeric variables.

```{r workflow}
random_forest_fitted$tuned_m$final_wf$pre$actions$recipe$recipe
```
# Defining your own model

The explicit versin of `dml_plr()` allows you to define your own model specifications using the `parsnip` package. Here I define a random forest regression model for the outcome variable and a random forest classification model for the treatment variable, then pass them to `dml_plr()`. 

```{r complex}
# Define the model for outcome


# Call dml_plr() with the explicit specs
fit <- dml_rf(
  data = mtcars |> dplyr::mutate(am = as.factor(am)),
  y = "mpg",
  d = "am",
  x = c("cyl", "disp", "hp", "drat", "wt", "qsec", "vs", "gear", "carb"),
)

print(fit)
```
